Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-02 hotstorage13/eval.tex
new experiment data

We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Objectives of our evaluation are:
1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.
2) Examine the impacts of buffering during metadata exchange.

@@

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O bandwidth of local storage is about 50MB/second 
in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
over 300MB/second with 4 drives or more and our setting uses
16.7\% or less of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster. 
%and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
%  For 2 hours, every machine can do 139MB/second. For 3 hours, then 92MB/second

% the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.

%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
%the effectiveness of CDS using real user VM disks from our production VM cluster.

%Since it's impossible to perform large scale analysis without affecting the VM performance,
%We have sampled a data set from 1323 real user VMs from a cluster with 100 nodes 
%to measure the effectiveness of our scheme.

%In this dataset, there are 10 snapshots per each VM user and the total amount of space 
%investigated is 17.5 terabytes.
%This dataset contas compose of 35 VMs from 7 popular OSes: 
%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
%5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
%The overall data size for this 700 full snapshots is 17.6 TB.
%This dataset  contains the snapshots of 1323 VMs.
%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
%study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
%
%using a dataset containing 10 snapshots of 35 VMs.
%Popularity of data blocks are collected through global counting 
%and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.

\comments{

Each VM file is  divided into content blocks of
variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using  their SHA-1 hash. 
Each segment is of size 2MB.  
Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
CDS every 1-2 days to catch up the popularity trend.
}
%seg, and we performed global perfect deduplication 
%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
%and maximum block size
%OS data
%user data: zipf
%prediction
%say something about aliyun

%To compare the effectiveness with a full deduplication approach with an approximation,
%we use  extreme binning and perfect deduplication~\cite{extreme_binning09}. 
%For perfect deduplication and extreme binning, each snapshot is also divided into chunk blocks
%using TTTD with an average size of 4KB. The original extreme binning work uses the whole file
%as the input unit and  this size is too big in our system. 
%Thus we split each image snapshot file into variable-sized segments base on the block hash list, 
%using TTTD with average size of 2MB.

%\subsection{Effectiveness of 3-level Deduplication}

%\begin{figure}
%  \centering
%  \epsfig{file=images/overall_effect.eps, width=3.5in}
%  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
%deduplication divided by the original data size and the unit is percentage. }
%
%  \label{fig:overall}
%\end{figure}

@@

\begin{table}[hbt]
\caption{ Performance when the number of partitions per machine node varies and $M$=35MB is imposed.}
\begin{center}
\begin{tabular} {|c|c|c|c|c|c|}
\hline \#Partitions  & 50 & 275  &450 &  750 &  1500 \\
\hline Index+request & 156&  28.4 & 17.4 & 10.7 & 5.2 \\
  (MB)           &  &   &  & &  \\

>>>>

We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
of Intel Nehalem E5530 machines.  
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Objectives of our evaluation are:
1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.
2) Examine the impacts of buffering during metadata exchange.

@@

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O bandwidth of local storage is about 50MB/second 
in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
over 300MB/second with 4 drives or more and our setting uses
16.7\% or less of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster.

@@

\begin{table}[hbt]
\caption{ Performance when the number of partitions per machine node varies and $M$=35MB is imposed.}
\begin{center}
\begin{tabular} {|c|c|c|c|c|c|}
\hline \#Partitions  & 100 & 250  & 500 &  750 &  1000 \\
\hline Index+request & 100.1 &  40.1 & 20.1 & 13.4 & 10.1 \\
  (MB)           &  &   &  & &  \\
